---
title: "Alcohol vs Seat choice"
author: "Kimberly Salazar"
date: "Fall 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```

   The front and the middle seat might look the same but the middle seats have more outliers. The back box is the median and is it also higher than the front and middle seat.
  


## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=davisdata)
```
## Inferential Tests
 The front and back seat have about the same amount of people compared to the people seated in the middle. Those seated in the middle are twice more than the front and back. The data chart tells me that while the back seat has 32 people the back seat has a max of 55 drinks and that is twice the number from the front and middle seat. The average drinks in the back seat is at 9.6 and the drinks for the front row people is about 2. The back seat has a median of about 3.
 
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
The possibility of getting this answer is one out of ten thousand. In order to see which seats are different from the others further investigation is needed.
 
```{r}
plot(TukeyHSD(model1),las=2)
```

The front and the back are different but the back and the middle are not different from each other but are different from the back. The back is different from the front and middle seat. 

## Conclusions


